Drought-sensitive trees survive on deep water access in a tropical forest community

### 2020-08-05 manuscript.rmd
edited source for hydraulic traits figure

```{r erd-hyd, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "60%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-erd-hyd}Modelled Effective Rooting Depth (ERD; mean $\\pm$ 1SE in m) versus hydraulic properties for eight large, canopy species found on Barro Colorado Island (Panama). *R*^2^ and *P*-values are given in panel insets.[X-Axis labels to be added: $K_{max}$ units as in Fig. 2. Water Potentials are in MPa.]")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/Select_traits_depth.jpeg"))
```

>>>>

```{r erd-hyd, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "60%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-erd-hyd}Modelled Effective Rooting Depth (ERD; mean $\\pm$ 1SE in m) versus hydraulic properties for eight large, canopy species found on Barro Colorado Island (Panama). *R*^2^ and *P*-values are given in panel insets.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/erd.stem.traits.jpeg"))
```
